Total Score

### 2023-04-27 src/MSAtotal_scores.Rmd
updated bar chart axis and criteria names

```{r}
# creating a function with criteria data and weight inputs
calculate_wt_criteria <- function(data, weights){
    wt_criteria <- data %>%
      # multiply each criteria by respective weight
      mutate(wt_real_estate = real_estate_score * weights[1],
             wt_landlord_policy = landlord_score * weights[2], 
             wt_solar_irr = financial_score * weights[3],
            wt_co2 = co2_score * weights[4], 
             wt_health_impacts = health_impact_score * weights[5],
             wt_electricity = electricity_score * weights[6],
             wt_climate_risk = climate_risk_score * weights[7]) %>% 
      # select weighted columns and rename them
      select(!c(ends_with("_score"))) %>%
      # create column for investment score
      mutate(investment_score = 0) %>%
      # for loop to sum weighted columns for each row
      mutate(investment_score = apply(.[, 4:10], 1, sum)) %>% 
      rename("Real Estate"="wt_real_estate",
             "Landlord Policy"="wt_landlord_policy",
             "Electricity Production"="wt_electricity", 
             "CO2 Emission Reduction"="wt_co2",
             "Climate Risk Avoided"="wt_climate_risk",
             "Health Impacts"="wt_health_impacts", 
             "Solar IRR"="wt_solar_irr") %>%  
      unite("msa_state", city_msa:state, sep = ", ")
 }

@@

```{r tidy data}
# client weights
wt_criteria_client <- calculate_wt_criteria(criteria_all, client_weights)  %>%  
  unite("msa_state", city_msa:state, sep = ", ")

@@

# equity weights
wt_criteria_equity <- calculate_wt_criteria(criteria_all, equity_weights) %>% 
  unite("msa_state", city_msa:state, sep = ", ")

@@

```{r client data viz}
tiff(filename = "client_criteria_barchart.tiff",width = 8, height = 6, units = "in", res = 300, pointsize = 12)
ggplot(data = client_score_tidy, aes(y = reorder(msa_state,  wt_criteria_score, FUN=sum), x = wt_criteria_score)) +
    geom_col(aes(fill = factor(criteria, levels = c("Climate Risk Avoided", "CO2 Emission Reduction", "Electricity Production", "Solar IRR", "Real Estate", "Landlord Policy", "Health Impacts")))) +
  theme_bw() +
  labs(x = "Total Score",
       y = " ",
       title = "") +
  guides(fill=guide_legend(title="Criteria (weighted)")) +
   scale_fill_manual(values = c("palevioletred1","orange",  "gold", "#44AA99", "dodgerblue4", "#BC80BD", "#6495ED"),
      breaks = c("Climate Risk Avoided", "CO2 Emission Reduction", "Electricity Production", "Solar IRR", "Real Estate", "Landlord Policy", "Health Impacts")) +
        scale_x_continuous(limits = c(0, 0.8), expand = c(0,0), breaks=seq(0, 0.8, 0.1)) 
#+ theme(legend.position = "none")
dev.off()
```

@@

#tiff(filename = "wt_criteria_student_chart.tiff", width = 8, height = 6, units = "in", res = 300)
 ggplot(data = equity_tidy, aes(y = reorder(msa_state, wt_criteria_score, FUN=sum), x = wt_criteria_score)) + 
    geom_col(aes(fill = criteria)) +
  labs(x = "Total Score",
       y = " ",
       title = "") +
  theme_bw() +
  guides(fill=guide_legend(title="Criteria (weighted)")) +
   scale_fill_manual(values = c("palevioletred1","orange",  "gold", "#44AA99", "dodgerblue4", "#BC80BD", "#6495ED"),
      breaks = c("Climate Risk Avoidance", "CO2 Abatement", "Electricity Production", "Solar IRR", "Real Estate", "Landlord Policy", "Health Impacts")) +
  scale_x_continuous(limits = c(0, 1.0), expand = c(0,0), breaks=seq(0, 1.0, 0.1))

@@

```{r}
library(patchwork)

@@

Figure 1. Ranked metropolitan areas (n=29) based on investment favorability for rooftop solar PV on mutlifamily houses. Areas were scored using six criteria, each given a respective weight given stakeholder priorities. Each criteria is comprised of indicator metrics using data from the U.S. Census Bureau and NREL's reOpt tool. Graph A represents a real estate investor stakeholder who prioritizes climate risk due to long-term investments. B represents a equity-focused stakeholder who values impacts on the community, emissions, and

>>>>

```{r}
# creating a function with criteria data and weight inputs
calculate_wt_criteria <- function(data, weights){
    wt_criteria <- data %>%
      # multiply each criteria by respective weight
      mutate(wt_real_estate = real_estate_score * weights[1],
             wt_landlord_policy = landlord_score * weights[2], 
             wt_solar_irr = financial_score * weights[3],
            wt_co2 = co2_score * weights[4], 
             wt_health_impacts = health_impact_score * weights[5],
             wt_electricity = electricity_score * weights[6],
             wt_climate_risk = climate_risk_score * weights[7]) %>% 
      # select weighted columns and rename them
      select(!c(ends_with("_score"))) %>%
      # create column for investment score
      mutate(investment_score = 0) %>%
      # for loop to sum weighted columns for each row
      mutate(investment_score = apply(.[, 4:10], 1, sum)) %>% 
      rename("Real Estate"="wt_real_estate",
             "Landlord Policy"="wt_landlord_policy",
             "Electricity Generation"="wt_electricity", 
             "Avoided CO2 Emissions"="wt_co2",
             "Climate Risk Avoided"="wt_climate_risk",
             "Avoided Health Costs"="wt_health_impacts", 
             "Solar Financials"="wt_solar_irr") %>%  
      unite("msa_state", city_msa:state, sep = ", ")
 }

@@

```{r tidy data}
# client weights
wt_criteria_client <- calculate_wt_criteria(criteria_all, client_weights)

@@

# equity weights
wt_criteria_equity <- calculate_wt_criteria(criteria_all, equity_weights)

@@

```{r client data viz}
tiff(filename = "client_criteria_barchart.tiff",width = 8, height = 6, units = "in", res = 300, pointsize = 12)
ggplot(data = client_score_tidy, aes(y = reorder(msa_state,  wt_criteria_score, FUN=sum), x = wt_criteria_score)) +
    geom_col(aes(fill = factor(criteria, levels = c("Climate Risk Avoided", "Avoided CO2 Emissions", "Electricity Generation", "Solar Financials", "Real Estate", "Landlord Policy", "Avoided Health Costs")))) +
  theme_bw() +
  labs(x = "Investment Favorabliity Score",
       y = " ",
       title = "") +
  guides(fill=guide_legend(title="Criteria (weighted)")) +
   scale_fill_manual(values = c("palevioletred1","orange",  "gold", "#44AA99", "dodgerblue4", "#BC80BD", "#6495ED"),
      breaks = c("Climate Risk Avoided", "Avoided CO2 Emissions", "Electricity Generation", "Solar Financials", "Real Estate", "Landlord Policy", "Avoided Health Costs")) +
        scale_x_continuous(limits = c(0, 0.8), expand = c(0,0), breaks=seq(0, 0.8, 0.1)) 
#+ theme(legend.position = "none")
dev.off()
```

@@

#tiff(filename = "wt_criteria_student_chart.tiff", width = 8, height = 6, units = "in", res = 300)
 ggplot(data = equity_tidy, aes(y = reorder(msa_state, wt_criteria_score, FUN=sum), x = wt_criteria_score)) + 
  geom_col(aes(fill = factor(criteria, levels = c("Climate Risk Avoided", "Avoided CO2 Emissions", "Electricity Generation", "Solar Financials", "Real Estate", "Landlord Policy", "Avoided Health Costs")))) +
  labs(x =  "Investment Favorabliity Score",
       y = " ",
       title = "") +
  theme_bw() +
  guides(fill=guide_legend(title="Criteria (weighted)")) +
   scale_fill_manual(values = c("palevioletred1","orange",  "gold", "#44AA99", "dodgerblue4", "#BC80BD", "#6495ED"),
      breaks = c("Climate Risk Avoided", "Avoided CO2 Emissions", "Electricity Generation", "Solar Financials", "Real Estate", "Landlord Policy", "Avoided Health Costs")) +
  scale_x_continuous(limits = c(0, 0.8), expand = c(0,0), breaks=seq(0, 0.8, 0.1))

@@

```{r COMBINED BAR CHARTS}
library(patchwork)

@@
